Notes on Perturbational Quantities

### 2011-06-16 docs/pert_notes/pert.tex
almost there...

We define $h = (rho h)^{(1)}/rho^{(1)}$.  Then we predict $h$ to edges
using {\tt make\_edge\_scal} in {\tt enthalpy\_advance} and the
underbraced term in Eq.~\ref{h equation labeled} as the forcing (see
also table~\ref{table:pred:hforce}).  This force is computed by
{\tt mkrhohforce} and then divided by $\rho$.  Note: {\tt mkrhoforce}
knows about the different {\tt enthalpy\_pred\_type}s and computes
the correct force for this type.

@@

We use the same procedure described in Section \ref{Computing rho at
  edges} to computing $\rho$ at edges from $\rho_0$ and
$\rho'_\mathrm{edge}$ and then multiply by $h_\mathrm{edge}$.

@@

@@

@@

\begin{table*}[h]
\begin{center}
\caption{When predicting temp ... (conversion done by {\tt makeRhoHfromT}) \newline}
\begin{tabular}{c|c|c|c}
\hline
\hline
{type} & {Inputs } & {EOS inputs} & {output} \\
\hline
3 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ &  $(\rho h)^\prime = \rho h - (\rho h)_0$ \\
   &                   & $   X = $ given & \\
   &                   &                 & \\
 4 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ & $h$ \\
   &                   & $   X = $ given & \\
   &                   &                 & \\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}[h]
\begin{center}
\caption{Quantity that is created in {\tt mkflux} and passed into {\tt update\_scal}\newline\
}
\begin{tabular}{c|c|c|c|c}
       &            &              &\multicolumn{2}{c}{Forcing Term} \\
{type} & {Species } & {$(\rho h)$} & {$(\rho X)$} & {$(\rho h)$} \\
\hline 
1 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
2 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
3 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}$ \\[2mm]
4 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

We define $h = (\rho h)^{(1)}/\rho^{(1)}$.  Then we predict $h$ to edges
using {\tt make\_edge\_scal} in {\tt enthalpy\_advance} and the
underbraced term in Eq.~\ref{h equation labeled} as the forcing (see
also table~\ref{table:pred:hforce}).  This force is computed by
{\tt mkrhohforce} and then divided by $\rho$.  Note: {\tt mkrhoforce}
knows about the different {\tt enthalpy\_pred\_type}s and computes
the correct force for this type.

@@

We use the same procedure described in Section \ref{Computing rho at
  edges} to computing $\rho_\mathrm{edge}$ from $\rho_0$ and
$\rho'_\mathrm{edge}$ and then multiply by $h_\mathrm{edge}$.

@@

\subsubsection{Predicting $T$ at edges}

We predict $T$ to edges using {\tt make\_edge\_scal} in {\tt
  enthalpy\_advance} and the underbraced term in Eq.~\ref{T equation
  labeled} as the forcing (see also table~\ref{table:pred:hforce}).
This force is computed by {\tt mktempforce}.

\subsubsection{Converting $T_\mathrm{edge}$ to $(\rho h)'_\mathrm{edge}$}

We the use EOS in {\tt makeHfromRhoT\_edge} (called from {\tt
  enthalpy\_advance}) to convert from $T_\mathrm{edge}$ to $(\rho
h)'_\mathrm{edge}$.  For the EOS call, we need $X_\mathrm{edge}$ and
$\rho_\mathrm{edge}$.  This construction depends on {\tt
  species\_pred\_type}, since the species edge states may differ
between the various prediction types (see the ``species quantity''
column in table~\ref{table:pred:hoverview}).  The EOS inputs are
constructed as:

\begin{table*}[h]
\centering
\caption{EOS states in {\tt makeHfromRhoT\_edge}\newline}
\label{table:pred:hforce}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c|c}
\hline
\hline
{\tt species\_pred\_type} & {$\rho$ edge state} &   {$X$ edge state}  \\
\hline
{\tt predict\_rhoprime\_and\_X} & 
  $\rho_0^{n+\myhalf,\rm{avg}} + \rho'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$ \\
{\tt predict\_rhoX} & 
  $\rho_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}/\rho_\mathrm{edge}$ \\
\hline
\end{tabular}
\end{table*}

The output of  {\tt makeHfromRhoT\_edge} is $(\rho h)'_\mathrm{edge}$.

The computation of the final $(\rho h)$ edge state is done identically
as the {\tt predict\_rhohprime} version.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt enthalpy\_pred\_type} = {\tt predict\_T\_then\_h}}

@@

\subsubsection{Predicting $T$ at edges}

The prediction of $T$ to the edges is done identically as the
{\tt predict\_T\_then\_rhohprime} version.

\subsubsection{Converting $T_\mathrm{edge}$ to $(\rho h)'_\mathrm{edge}$}

This is identical to the {\tt predict\_T\_then\_rhohprime} version,
except that on output, we compute $h_\mathrm{edge}$.

The computation of the final $(\rho h)$ edge state is done identically
as the {\tt predict\_h} version.

@@

%% \begin{table*}[h]
%% \begin{center}
%% \caption{When predicting temp ... (conversion done by {\tt makeRhoHfromT}) \newline}
%% \begin{tabular}{c|c|c|c}
%% \hline
%% \hline
%% {type} & {Inputs } & {EOS inputs} & {output} \\
%% \hline
%% 3 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ &  $(\rho h)^\prime = \rho h - (\rho h)_0$ \\
%%    &                   & $   X = $ given & \\
%%    &                   &                 & \\
%%  4 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ & $h$ \\
%%    &                   & $   X = $ given & \\
%%    &                   &                 & \\
%% \hline
%% \end{tabular}
%% \end{center}
%% \end{table*}

%% \begin{table*}[h]
%% \begin{center}
%% \caption{Quantity that is created in {\tt mkflux} and passed into {\tt update\_scal}\newline\
%% }
%% \begin{tabular}{c|c|c|c|c}
%%        &            &              &\multicolumn{2}{c}{Forcing Term} \\
%% {type} & {Species } & {$(\rho h)$} & {$(\rho X)$} & {$(\rho h)$} \\
%% \hline 
%% 1 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
%% 2 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
%% 3 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}$ \\[2mm]
%% 4 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
%% \hline
%% \end{tabular}
%% \end{center}
%% \end{table*}
